\subsection{Unified Modeling Language}
\acrfull{uml} is \textit{``A specification defining a graphical language for visualising, specifying, constructing, and documenting the artifacts of distributed object systems.''}~\cite{OMG2017About2.5.1}. The latest version of the specification is \acrshort{uml} 2.5.1 which was published in 2017. It is describes a set of diagrams and their standardised notations, which are used in software system and business modelling, as well as other non-software modelling tasks. In total 14 \acrshort{uml} diagrams are defined. There are two principal types of diagrams: \textit{Behaviour} and \textit{Structure} diagrams~\cite{ObjectManagementGroup2015Unified2.5}. Main difference between the two is that Behaviour diagrams indicate system's objects dynamic behaviour and Structure diagrams indicate their static structure. In this project, we have use one structure diagram -- a class diagram and two behaviour diagrams -- use case and sequence diagrams, which help us to visualise flows in the system and document the implemented prototype.

\subsubsection{Class diagram}
Class diagram is a static diagram which specifies the structure of the system. It is used for detailed modelling of the application's structure by visualising all classes, containing the name, attributes and operations of the class, and static relationships between them. Detailed and well designed class diagram can afterwards be translated to a programming code. Designing a class diagram before programming can help to structure the code better and save time during the programming phase. The class diagram can also be used to document the existing code~\cite{Seidl2015UMLModeling}.

\subsubsection{Use case diagram}
Use case diagram is a behaviour diagram which describes the interaction of an external user with a system. Main components of a use case diagram are use cases, actors, associations. Actors are external users, humans or other systems, who are interacting with the system. Actors may proactively request services from the system, or may react to requests made by the system~\cite[p.~28]{Cockburn2000WritingCases}. Use cases depict a possible scenarios and use of a system which an actor can come across and are drawn in ovals. Associations are relations between use cases and actors. Use case diagram helps us to visualise all actors of our system, both humans and external systems, to know and see with which use cases are they interacting with, and where are the boundaries of our system.

\subsubsection{Sequence diagram}
Sequence diagram is a behaviour diagram describing the interaction between objects and their message exchange in sequence. It consists of vertical lines known as lifelines which represent objects and processes that run in parallel, and horizontal lines which represents messages that are being interchanged in sequence. We use the sequence diagram to demonstrate message exchange between entities of our system in a few basic scenarios.